\subsection{REST API Summary}

%describe the REST API. If needed, add a few lines of text here, describing the content of the table.

The list of the rest API for this homework are still “in progress” because we have to decide according
to the frontend where is better to use a REST call or not.
Anyway, there are some resources that are just available with REST that are reported in the next
table.
\\
\\
The rest API is studied to experiment with multiple different approaches to the REST paradigm. More in detail,
endpoints associated with rides and devices are developed in a more traditional way, with the entirety of the
information needed to satisfy the request directly in the URI. Other endpoints require additional information
(such as the type of operation required) as additional parameters in the request.
\\
\\
Part of the URIs are filtered through different filters. S indicates that only users with the role of student
can access to the endpoint, T indicates that only T can access the endpoint, A that only administrators
can request the specified URI to the server.
\\

\begin{longtable}{|p{.375\columnwidth}|p{.1\columnwidth} |p{.35\columnwidth}|p{.1\columnwidth}|} 

\hline
\textbf{URI} & \textbf{Method} & \textbf{Description} & \textbf{Filter} \\

\hline
    %URI
admin/   
&   % Method
POST
&   %Description
Go to the administrator section. Only admin can see access the infomation
&   %ROLE
A\\
\hline

\hline
    %URI
admin/dashboard/
&   % Method
POST
&   %Description
Go to the administrator dashboard. Only admin login.
&   %ROLE
A\\
\hline

\hline
    %URI
login/   
&   % Method
POST
&   %Description
Go to login section for teacher and students only
&   %ROLE
S and T\\
\hline

\hline
    %URI
register/   
&   % Method
POST
&   %Description
Go to registration section for teacher and students only
&   %ROLE
S and T\\
\hline

\hline
    %URI
home/   
&   % Method
POST
&   %Description
Go to homepage
&   %ROLE
S and T\\
\hline

\hline
    %URI
about-us/   
&   % Method
POST
&   %Description
Go to about us
&   %ROLE
S and T\\
\hline

\hline
    %URI
contact-us/   
&   % Method
POST
&   %Description
Go to contact us
&   %ROLE
S and T\\
\hline

\hline
    %URI
(user)/dashboard/
&   % Method
GET
&   %Description
Go to the administrator dashboard. Student and teacher can see access the infomation.
&   %ROLE
S and T\\
\hline

\hline
    %URI
(user)/search/(course-name)
&   % Method
GET
&   %Description
Search for the course
&   %ROLE
S and T\\
\hline

\hline
    %URI
(user)/(course-id) 
&   % Method
GET
&   %Description
Go to the course for information
&   %ROLE
S and T\\
\hline

\hline
    %URI
(user)/(course-id)/enroll
&   % Method
POST
&   %Description
Enroll in a course
&   %ROLE
S\\
\hline

\hline
    %URI
(user)/(course-id)/unenroll
&   % Method
POST
&   %Description
Un-enroll in a course
&   %ROLE
S\\
\hline

\hline
    %URI
teacher/(course-id)/post
&   % Method
GET
&   %Description
Post material for a course
&   %ROLE
T\\
\hline

\hline
    %URI
student/(teacher-id)/message
&   % Method
POST
&   %Description
Message a teacher
&   %ROLE
T\\
\hline


\caption{Describe in this table your REST API}
\label{tab:termGlossary}
\end{longtable}