\section{Main Functionalities}
TORE- Learning Management System will allow students and teachers to interact with each other in an easy way to share study material and enquiries creating a central platform. Major functionalities will be as following
\begin{enumerate}
    \item \textbf{\underline {Main Area}}. Accessible to everyone interested in knowing about the system and will be used for registering new users and signing up existing users.
    \item \textbf{\underline {Admin Area}}. This area will only be accessible to users with admin rights. It will hold following functionalities.
    \begin{itemize}
        \item Approval of all users registering for the system.
        \item Maintenance of profiles according to type of account.
        \item Maintenance of Database.
        \item Assignment of tasks to teacher accounts.
        \item Maintenance of subject allotment to teachers.
    \end{itemize}
    \item \textbf{\underline {Faculty Area}}. This area will be restricted for the use of teachers only and will perform following
     \begin{itemize}
        \item Each teacher will be able to access his own specified subjects.
        \item Teacher will have the authority to manage students and course contents.
        \item Management of student affairs including enrolment.
        \item Replying to the comments/ questions made by the students.
    \end{itemize}
    \item \textbf{\underline {Students Area}}. This area will be accessible to all users registered as students and will offer following functionalities
    \begin{itemize}
        \item Enrolment to subjects/ courses.
        \item Viewing contents shared by teachers of each course.
        \item Submitting questions/ commenting on course contents.
    \end{itemize}
\end{enumerate}
Major roles of different users will be following
\begin{enumerate}
    \item Admin.  Responsible for over all management and approval of all users registering.
    \item Teachers.  Will be able to deal with subjects allotted by admin and enrol students.
    \item Students.  Can register and enrol into subjects offered after approval from admin.
\end{enumerate}