\section{Presentation Logic Layer}
\graphicspath{ {./HW_1/images/} }
%What pages will be present in your project? briefly indicate how your web site will be organized

The website will be divided into the following pages:
\begin{itemize}
    \item Homepage: contains the main area with the sections AboutUs and ContactUs. Allows users to login or register to the system through LOGIN and REGISTER buttons, respectively. Developed via jsp.
    \item Login page: allows the users login to the web application. Developed via jsp.
    \item Registration page: allows the user to register to the web pages..
    \item Administration page: allows to administrate users’ accounts. Written in HTML.
    \item Teacher page: allows users to search for maintenance events. written in HTML with the
support of javascript.
    \item List students page: allows to insert a new maintenance event. Written in HTML.
    \item List teachers page: allows to upload a file containing the measurements. Written in HTML.
    \item Teacher dashboard page: allows to redirect users toward pages handling specific resources. Written in HTML.
    \item Available teachers page:
    \item About Us page:
    \item Contact Us page:
    \item Post material page:
    \item RegisterWireframePage:
    \item RequestCoursePage:
    \item StudentDashboardPage:
    \item SendQueryTeacherPage:
    \item SubjectAreaPage:
    \item 2 pages each to handle insertion and update of parks, rides and models. Written in HTML.
    
    \item A support page which displays messages upon completion of specific tasks, such as the removal or update
of resources.
\end{itemize}

\subsection{Login Form}

%For the main pages put a mockup and describe it in detail.

\input{sections/PLL/HomePage.tex}
\input{sections/PLL/LoginPage.tex}
\input{sections/PLL/StudentRegistrationPage.tex}
\input{sections/PLL/AdminPage.tex}
\input{sections/PLL/TeacherPage.tex}
\input{sections/PLL/ListStudentsPage.tex}
\input{sections/PLL/ListTeachersPage.tex}
\input{sections/PLL/TeacherDashboardPage.tex}
\input{sections/PLL/AvailableTeachersPage.tex}
\input{sections/PLL/AboutUsPage.tex}
\input{sections/PLL/ContactUsPage.tex}
\input{sections/PLL/PostMaterialPage.tex}
\input{sections/PLL/RegisterWireframePage.tex}
\input{sections/PLL/RequestCoursePage.tex}
\input{sections/PLL/StudentDashboardPage.tex}
\input{sections/PLL/SendQueryTeacherPage.tex}
\input{sections/PLL/SubjectAreaPage.tex}

